% !TeX root = ./fragment_II.tex
%
\lettrine[lines=3]{\junicode{\textcolor{crimson}{L}}}{ast} night I had a severe
headache most likely due to irregular caffeine intake.  However, I did not
perform \emph{Z1} in that evening,  so I decided to test the idea that my
headache was partially or fully due to my missing the evening \emph{Z1}; that
$\mathfrak{Babalon}$ was communicating to me thru the pain of the headache that
I must not skip a dedication to Her.


I hesitate to call this punishment---rather I would call it communication with
a high signal-to-noise ratio.  If She communicated via a pleasurable RSR, it
would have been unclear as to the reason for its occurrence, except the
possibility that She was providing comfort.

Why the severity?  If the severity was normal I would not have considered it a
possible communication.  Hence, it needed to be an abnormal pain level so that
there could be a possibility of me considering it a message from
$\mathfrak{Babalon}$.

To test the idea that this was a communication from Our Lady, stating that I
must not miss a planned devotion, I made an offering of my semen to Her in line
with sex magick practices of Thelema and Ophidian Thelema---this offering was
the first thought that came to mind when I considered what to offer.

\paragraph{Operation:} I opened her shrine, lit the altar candle and offered
incense.  I masturbated as I chanted 2AC and after the last line after the
third cycle of the chant, I made my offering into Her Cup of Fornication while
saying \emph{In Nomine Babalon}. I blew out the candle and disposed of my
offering. I washed Her Cup, added fresh water and returned it to the altar.  I
went back to bed.

\paragraph{}\noindent The pain, which was throughout my head, now was localized to just
my left side. However, the severity did not subside.  Not able to bear the
pain, I took a Quitiepine and GABApentine to put me to sleep. I woke up around
06:45.  The headache was gone, but it was in the background.

\paragraph{Conclustion:} The experiment gives a small plausibility to the
communication hypothesis given that the pain did localize to the left side.
Could this be signaling the Left-Hand Path of which sex magick is a component
part?  My expectation was that the pain before the offering would be symmetric
to the pain after the offering; that is, much less.  But a full head of pain
does not feel symmetric to a half a head of pain of equal severity.

The operation, I think, was most likely not a communication from
$\mathfrak{Babalon}$.  And the method of offering was probably an idea from my
own sexual desire and from reading about the sex magick practices in the
O.T.O., not a suggestion from Her.  This does not de-legitimize nor diminish
nor trivialize my offering, however---it was a powerful, sincere token of my
devotion.  To Her it is my most precious physical possession.


